---
title: "p8105_hw6_sl4471"
author: Shuwei Liu
date: 11/23/2018
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 6.5,
  fig.asp = 1.0,
  out.width = "90%"
)
library(tidyverse)
library(modelr)
library(mgcv)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

# Probelm 1

```{r import_and_tidy}
homicides_data = 
  read_csv("./data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(city_state = str_c(city, ", ",  state), 
         resolved = as.numeric(disposition == "Closed by arrest"), 
         victim_race = ifelse(victim_race == "White", "White", 
                              ifelse(!(victim_race == "White"), "Non-white", NA)),
         victim_race = fct_relevel(victim_race, "White"), 
         victim_age = as.numeric(victim_age)) %>% 
  filter(!(city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")))
```

```{r baltimore_fit}
baltimore_fit = 
  homicides_data %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial())

baltimore_estimate =
  baltimore_fit %>% 
  broom::tidy()
```


```{r or_ci}
baltimore_or = 
  baltimore_fit %>% 
  broom::tidy(conf.int = TRUE, exponentiate = TRUE) %>% 
  rename(OR = estimate) %>% 
  select(OR, conf.low, conf.high) %>% 
  bind_cols(baltimore_estimate, .) %>% 
  filter(term == "victim_raceNon-white") %>% 
  select(term, estimate, OR, conf.low, conf.high)

knitr::kable(baltimore_or, digits = 3)
```


```{r all_cities, warning = FALSE}
glm_all = 
  homicides_data %>% 
  group_by(city_state) %>% 
  nest() %>% 
  mutate(model_glm = map(data, ~glm(resolved ~ victim_age + victim_race + victim_sex, 
                                 data = ., family = binomial())),
          tidy_glm = map(model_glm, broom::tidy), 
         ci_glm = map(model_glm, broom::confint_tidy)) %>% 
  select(-data, -model_glm) %>% 
  unnest() %>% 
  filter(term == "victim_raceNon-white") %>% 
  mutate(OR = exp(estimate), conf.low = exp(conf.low), conf.high = exp(conf.high)) %>% 
  select(city_state, OR, conf.low, conf.high)

glm_all
```

```{r all_plot}
glm_all %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) +
  geom_point(color = "red") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), alpha = 0.5) +
  coord_flip() +
   labs(
    title = "The odds ratio and CIs of each city",
    x = "City",
    y = "Odds Ratio and CI") +
  theme(axis.text.y = element_text(size = 8, hjust = 1)) 
```

From the plot, the odds ratios of Tamlpa, Birmingham and Durham are equal to or greater than 1 while those of most cities are less than 1. This result shows that cases with non-white victim are less likely to be solved in most cities than those with white victim. Although Tamlpa, Birmingham and Durham have a higher odds ratio, they also have a pretty wide confidence inverval which makes the estimates have a bad performance in accuracy.

# Problem 2

```{r}
birthweight = 
  read_csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  select(bwt, everything()) %>% 
  mutate(babysex = as.factor(ifelse(babysex == 1, "Male", "Female")), 
         frace = as.factor(ifelse(frace == 1, "White", 
                                  ifelse(frace == 2, "Black", 
                                         ifelse(frace == 3, "Asian", 
                                                ifelse(frace == 4,
                                                       "Puerto Rican", 
                                                       ifelse(frace == 8, "Other", 
                                                              ifelse(frace == 9, "Unknown",
                                                                     NA))))))),
         frace = fct_relevel(frace, "White"),
         malform = as.factor(ifelse(malform == 0, "Absent", "Present")),
         mrace = as.factor(ifelse(mrace == 1, "White", 
                                  ifelse(mrace == 2, "Black", 
                                         ifelse(mrace == 3, "Asian", 
                                                ifelse(mrace == 4,
                                                       "Puerto Rican", 
                                                       ifelse(mrace == 8, "Other", NA)))))),
         mrace  = fct_relevel(mrace, "White"))


table(is.na(birthweight))
```

```{r}
birthweight_fit = lm(bwt ~ ., data = birthweight)
step(birthweight_fit, direction = 'backward')
```

```{r}
model1 = lm(bwt ~ babysex + bhead + blength + delwt + 
              fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight)
summary(model1)
```

```{r}
birthweight %>% 
  add_predictions(model1) %>% 
  add_residuals(model1) %>%
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = 0.5) +
  labs(
    title = "Residuals VS Fitted values",
    x = "Fitted value",
    y = "Residual")
```

```{r}
model2 = lm(bwt ~ blength + gaweeks, data = birthweight)
summary(model2)
```

```{r}
model3 = lm(bwt ~ bhead + blength + babysex + babysex*bhead + 
              babysex*blength + bhead*blength + babysex*bhead*blength, data = birthweight)
summary(model3)
```


```{r}
cv_df = 
  crossv_mc(birthweight, 100) %>% 
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble)) %>% 
  mutate(model1 = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + 
              fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = birthweight)),
         model2 = map(train, ~lm(bwt ~ blength + gaweeks, data = birthweight)),
         model3 = map(train, ~lm(bwt ~ bhead + blength + babysex + babysex*bhead + 
              babysex*blength + bhead*blength + babysex*bhead*blength, data = birthweight))) %>% 
  mutate(rmse_model1 = map2_dbl(model1, test, ~rmse(model = .x, data = .y)),
         rmse_model2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)),
         rmse_model3 = map2_dbl(model3, test, ~rmse(model = .x, data = .y)))
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  gather(key = model, value = rmse) %>% 
  mutate(model = str_replace(model, "rmse_", ""),
         model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin(fill = "blue", alpha = 0.5)
```

